---
title: "Week 5 Lab"
author: Jessica Tran
date: today 
title-block-banner: true
theme: spacelab
format: html
editor: visual
---

## Data

For this lab, we will be using the data set `CO2`. Take some time to get familiar with the data set using the help function.

```{r}
?CO2
```

## Problem 1

Conduct a hypothesis test for a mean of one sample. Using the data set `CO2`and the variable `uptake`, test the null hypothesis that the population mean `uptake` is mean 28 vs. the alternate hypothesis that the population mean `uptake` is less than 28 with a significance level of 0.05.

Check any assumptions:

```{r}
qqnorm(CO2$uptake)  
qqline(CO2$uptake)
```

If the assumptions are met, calculate the p-value:

```{r}
t.test(CO2$uptake, mu = 28, alternative = "less", conf.level = 0.95)
```

## Problem 2

Conduct a hypothesis test for independent samples. Use the data set `CO2` and the variables `Type` and `uptake`. Let group 1 be `Quebec`and group 2 be `Mississippi`. Test the null hypothesis that the population mean `uptake` of the `Quebec` samples is the **same** as that of the `Mississippi` samples vs. the alternate hypothesis that the population mean `uptake` of the `Quebec` samples is **different** than that of the `Mississippi` samples with a significance level of 0.01. Comment out each line of code to explain what you are doing.

Check any assumptions:

```{r}
group1 <- with(CO2, uptake[Type == "Quebec"]) # select just group 1
group2 <- with(CO2, uptake[Type == "Mississippi"]) # select just group 2

qqnorm(group1)                           # QQ plot for group 1
qqline(group1)

qqnorm(group2)                           # QQ plot for group 2
qqline(group2)

var.test(group1, group2)
```

If the assumptions are met, calculate the p-value:

```{r}
t.test(uptake ~ Type, data = CO2, alternative = "two.sided", conf.level = 0.99, paired = FALSE, var.equal = TRUE)
```

## Problem 3

Conduct a hypothesis test for paired samples. Use the data set `CO2` and the variable `uptake`. Let group 1 be `chilled` and group 2 be `nonchilled`. Test the null hypothesis that the population mean `uptake`of the `chilled` samples is the same as that of the `nonchilled` samples vs. the alternate hypothesis that the population mean `uptake` of the `chilled` samples is different than that of the `nonchilled` samples with a significance level of 0.05. Comment out each line of code to explain what you are doing.

Check any assumptions:

```{r}
group1 <- with(CO2, uptake[Treatment == "chilled"]) # select just group 1
group2 <- with(CO2, uptake[Treatment == "nonchilled"]) # select just group 2

differenced_data <- group1 - group2     

qqnorm(differenced_data)
qqline(differenced_data)
```

If the assumptions are met, calculate the p-value:

```{r}
t.test(uptake ~ Treatment, data = CO2, alternative = "two.sided", conf.level = 0.95, paired = TRUE)
```

## Problem 4

Conduct a hypothesis test for one proportion. We are interested in knowing what proportion of plants have an uptake greater than 25 $\mu$mol/ $m^2$ sec. Out of the 84 plants, 49 of them had an uptake greater than 25 $\mu$mol/ $m^2$ sec. At a significance level of 1%, can you conclude that a majority of plants have an update greater than 25 $\mu$mol/ $m^2$ sec. Comment out each line of code to explain what you are doing.

Check any assumptions:

```{r}
84*(0.5)         #np
84*(1-0.5)     #n(1-p)
```

If the assumptions are met, calculate the p-value:

```{r}
prop.test(49, 84, p = 0.5, alternative = "greater", correct = FALSE)
```

## Submitting

Submit the following to Canvas:

-   Your rendered PDF titled Lastname_5R. Make sure your name is at the top of the document.

-   Your .qmd file
