---
title: "Week 7 Lab"
author: Jessica Tran
date: today 
title-block-banner: true
theme: spacelab
format: html
editor: visual
---

## Packages

We will need the following package for this lab:

```{r}
library(car)
```

## Data

For this lab, we will be using the data set `chickwts`. Take some time to get familiar with the data set using the help function.

```{r}
?chickwts
```

## Problem 1

Using the data set `chickwts`, test to see if there is any significant difference between the average `weight` of of chicks based on the factors `feed`. Use a significance level of 0.05

Conduct the test.

```{r}
output <- aov(weight ~ feed, data = chickwts)
```

Check the normality assumption.

```{r}
shapiro.test(output$residuals)
```

Check the equal variance assumption.

```{r}
leveneTest(output)
```

Check the independence assumption.

```{r}
set.seed(1)
durbinWatsonTest(output)
```

Display the results.

```{r}
summary(output)
```

If appropriate, perform a post hoc analysis.

```{r}
TukeyHSD(output)
```

## Submitting

Submit the following to Canvas:

-   Your rendered PDF titled Lastname_7R. Make sure your name is at the top of the document.

-   Your .qmd file
