---
title: "Week 6 Lab"
author: Jessica Tran
date: today 
title-block-banner: true
theme: spacelab
format: html
editor: visual
---

## Package Install

We will need the following package for this lab:

```{r}
library("survival")
```

## Data

For this lab, we will be using the data set `transplant`. Take some time to get familiar with the data set using the help function.

```{r}
?transplant
```

## Problem 1

Using the data file `transplant` and the variable `event`, which is a categorical variable with four categories, test to see if they are uniformly distributed, i.e., the probability that each problem type occurs is 1/4. Use a significance level of 0.05.

Check any assumptions:

```{r}
output <- chisq.test(table(transplant$event))
output$expected
```

If the assumptions are met, calculate the p-value:

```{r}
output$p.value
```

## Problem 2

Using the data file `transplant` and the variables `event`, which is a categorical variable with four categories, and `abo`, which is a categorical variable with blood type, test to see if they are independent. Use a significance level of 0.05. You will need to begin by creating a data frame with just those two columns. Ignore any `warnings`.

Check any assumptions:

```{r}

output <- chisq.test(table(transplant$event, transplant$abo))
output$expected
```

If the assumptions are met, calculate the p-value:

```{r}

```

## Submitting

Submit the following to Canvas:

-   Your rendered PDF titled Lastname_6R. Make sure your name is at the top of the document.

-   Your .qmd file
