---
title: "Week 4 Lab"
author: Jessica Tran
date: today 
title-block-banner: true
theme: spacelab
format: html
editor: visual
---

## Problem 1

Suppose a genetic condition is in 2% of the population. If you have the genetic condition, you are 100 times more likely to develop a specific type of cancer. Suppose you have a group of 4 patients who have cancer. Let `X` equal the number of cancer patients that have the genetic condition. Determine if this is a binomial distribution or a poisson distribution and find the corresponding PDF and a CDF in table form (that is, use `data.frame`).

```{r}
data.frame(
  "X" = 0:4,
  "PDF" = dbinom(c(0:4), 4, p = 0.02),
  "CDF" = pbinom(c(0:4), 4, p = 0.02)
)
```

Find the probability less than two patients have the genetic condition using either the PDF or the CDF.

```{r}
pbinom(1, 4, p = 0.02)
```

## Problem 2

The average exam score is normally distributed with mean 70 with a standard deviation of 4. Find the probability someone gets below a 60.

```{r}
pnorm(60, mean = 70, sd = 4)
```

## Problem 3

Suppose the price for generic ibuprofen is normally distributed with mean of \$5.00 and standard deviation of \$0.50. If the price you pay is the 90th percentile, how much are you paying for the ibuprofen?

```{r}
Z <- qnorm(.90)
5 + Z*0.5
```

## Problem 4

Find a 90% confidence interval for a random sample of twenty students who took a driving test where 65% of the student's passed. Make sure to check any assumptions. Comment out each line of code to explain what you are doing.

```{r}
phat <- 13/20        # sample proportion
n <- 20             # sample size
n*phat
n*(1-phat)
Z <- qnorm(1 - 0.1/2)               # z score
L1 <- phat - Z*sqrt(phat*(1-phat)/n) # lower endpt
L2 <- phat + Z*sqrt(phat*(1-phat)/n) # upper endpt
c(L1, L2) 
```

## Problem 5

Find a 95% confidence interval for a random sample of thirty highway speeds of cars on I-24 was taken. The data is below. Make sure to check any assumptions. Comment out each line of code to explain what you are doing.

|     |     |     |
|-----|-----|-----|
| 85  | 73  | 82  |
| 106 | 83  | 87  |
| 75  | 96  | 97  |
| 79  | 88  | 88  |
| 99  | 88  | 80  |
| 99  | 97  | 72  |
| 92  | 77  | 95  |
| 63  | 78  | 87  |
| 79  | 73  | 88  |
| 90  | 76  | 71  |

```{r}
speed <- c(85, 73, 82, 106, 83, 87, 75, 96, 97, 79, 88, 88, 99, 88, 80, 99, 97, 72, 92, 77, 95, 63, 78, 87, 79, 73, 88, 90, 76, 71)
qqnorm(speed)
qqline(speed)
xbar <- mean(speed)                # sample mean
t <- qt(0.95, df = 30 - 1)         # t score (1 - .05/2)
s <- sd(speed)                     # sample sd
n <- 30                             # sample size
L1 <- xbar - t*s/sqrt(n)            # lower endpt
L2 <- xbar + t*s/sqrt(n)            # upper endpt
c(L1, L2)
```

## Submitting

Submit the following to Canvas:

-   Your rendered PDF titled Lastname_4R. Make sure your name is at the top of the document.

-   Your .qmd file
