---
title: "Week 8 Lab"
author: Jessica Tran
date: today 
title-block-banner: true
theme: spacelab
format: html
editor: visual
---

## Packages

We will need the following packages for this lab:

```{r}
library("car") 
library("palmerpenguins")
```

## Data

For this lab, we will be using the data set `penguins`. Take some time to get familiar with the data set using the help function.

```{r}
?penguins
```

## Problem 1

Using the data set `penguins`, perform a Two Way ANOVA test to see if there is any significant difference between the average `body_mass_g` of the penguins based off the factor `species` and the group `sex`. Use a significance level of 0.05

First, check that `species` and `sex` are both factors using the `head` command. If necessary, convert your data to factors.

```{r}
head(penguins)
```

Now, conduct the test.

```{r}
output <- aov(body_mass_g ~ species + sex, data = penguins)
```

Check the normality assumption.

```{r}
shapiro.test(output$residuals)
```

Check the equal variance assumption.

```{r}
leveneTest(body_mass_g ~ species * sex, data = penguins)
```

Check the balanced assumption.

```{r}
table(penguins$species, penguins$sex)
```

Display the results.

```{r}
summary(output)
```

If appropriate, perform a post hoc analysis.

```{r}
TukeyHSD(output)
```

## Problem 2

Using the data set `penguins`, perform a Three Way ANOVA test to see if there is any significant difference between the average `body_mass_g` of the penguins based off the factor `species` and the group `sex`, and to determine if there is an interaction. Use a significance level of 0.05.

```{r}
output1 <- aov(body_mass_g ~ species * sex, data = penguins)
summary(output1)
```

## Submitting

Submit the following to Canvas:

-   Your rendered PDF titled Lastname_8R. Make sure your name is at the top of the document.

-   Your .qmd file
