---
title: "Week 2 Lab"
author: Jessica Tran
date: today 
title-block-banner: true
theme: spacelab
format: html
editor: visual
---

## Packages

We will need the following package for this lab:

```{r}
library(ggplot2)
```

## Data

For this lab, we will be using the data set `msleep`. We will explore this data set in Problem 1.

## Problem 1

We will be using the data set `msleep` for this. Explore the data set using the help function.

```{r}
?msleep
```

## Problem 2

Create a histogram for the variable `sleep_total`. Select a binwidth you think fits the data best. Change the color of the bars (hint: use `geom_histogram(binwidth = YOUR VALUE, fill = "YOUR COLOR")`. I suggest googling "ggplot 2 colors" for ideas. Change the axis labels to include capital letters, and add a title. Add a theme.

```{r}
ggplot(msleep, aes(sleep_total)) + 
  geom_histogram(binwidth = 1, fill = "pink3") +
  xlab("Hours of Sleep") +
  ylab("Number of Mammals") +
  ggtitle("Total Hours of Sleep for Mammals") +
  theme_classic()
```

## Problem 3

Create a boxplot for the variable `awake`. Change the color of the box (hint: use `geom_boxplot(fill = "your color"` ). I suggest goggling "ggplot 2 colors" for ideas. Change the axis label to include capital letters, and add a title. Add a different theme.

```{r}
ggplot(msleep, aes(awake)) +
  geom_boxplot(fill = "purple1") +
  xlab("Hours Spent Awake") +
  ggtitle("Total Hours Spent Awake by Mammals") +
  theme_minimal()
```

## Problem 4

Create a scatter plot for the variables `sleep_rem` and `sleep_total`. Plot the line of best fit and remove the confidence interval. Change the axis label to include capital letters, and add a title. Add a different theme. You may get a warning that a few rows were containing missing values and were ignored, that is normal!

```{r}
ggplot(msleep, aes(sleep_rem, sleep_total)) + 
  geom_point(colour = "skyblue1") +
  geom_smooth(method = "lm", se = F) +
  xlab("Hours of REM Sleep") +
  ylab("Total Hours of Sleep") +
  ggtitle("Correlation Between Hours of REM Sleep and Total Hours of Sleep") +
  theme_dark()
```

Now set `color = vore` inside your `aes()` function and see what happens. Make sure you change the title to distinguish between the previous graph.

```{r}
ggplot(msleep, aes(sleep_rem, sleep_total,color = vore)) + 
  geom_point() +
  geom_smooth(method = "lm", se = F) +
  xlab("Hours of REM Sleep") +
  ylab("Total Hours of Sleep") +
  ggtitle("Relationship Between Hours of REM Sleep and Total Hours of Sleep") +
  theme_light()
```

## Problem 5

Create a bar chart for the variable `vore`. Change the color of the bars. Change the axis label to include capital letters, and add a title. Add a different theme.

```{r}
ggplot(msleep, aes(vore)) +
  geom_bar(fill = "pink") +
  xlab("Vore") +
  ylab("Number of Mammals") +
  ggtitle("Types of Genus in Mammals") +
  theme_bw()
```

## Submitting

Submit the following to Canvas:

-   Your rendered PDF titled Lastname_2R. Make sure your name is at the top of the document.

-   Your .qmd file
